Estimating the Initial Susceptible Fraction in Dengue Dynamics

### 2014-11-20 draft_lm1.tex
Minor fixes to table
it's != its

In this section we will start by describing how we estimated the effective 
reproductive number, $R_t$, relative to the global dengue cases, and it's 
posterior probability distribution. 
We then proceed to describe the SIR model 
used to represent the global incidence and how the $R_t$ is integrated into the 
model to allow for time varying transmission. 
Then we describe the Bayesian 
estimation methodology applied to find the posterior probability distributions 
of the susceptibles to the main circulating Dengue viruses for each epidemic, 
using Dengue incidence time series for Rio de Janeiro from 1996 to 2014.
In the last subsection we describe how we estimated the Attack ratio of each 
epidemic from the estimated susceptibility and observed incidence.

@@

\begin{table}[!ht]
\caption{
\bf{Median Attack ration calculated according to (\ref{eq:AR2})}}
\begin{center}
\begin{tabular}{l|r}
\hline
Year & Median Attack Ratio \\
\hline
1996 & \textbf{38.64\%} (17.18\%-54.19\%)\\
1997 & \textbf{87.31\%} (73.83\%-87.31\%)\\
1998 & \textbf{49.86\%} (49.19\%-49.86\%)\\
1999 & \textbf{10.76\%} (3.72\%-20.24\%)\\
2000 & \textbf{25.49\%} (24.47\%-26.98\%)\\
2001 & \textbf{48.12\%} (46.57\%-49.15\%)\\
2005 & \textbf{14.74\%} (10.23\%-21.38\%)\\
2006 & \textbf{11.22\%} (8.00\%-14.41\%)\\
2007 & \textbf{15.08\%} (14.76\%-15.38\%)\\
2008 & \textbf{13.73\%} (3.10\%-30.84\%)\\
2010 & \textbf{18.30\%} (17.34\%-19.33\%)\\
2011 & \textbf{8.59\%} (8.20\%-9.36\%)\\
2012 & \textbf{13.92\%} (12.71\%-14.92\%)\\
\hline
\end{tabular}
\begin{flushleft}Medians are presented with 95\% credible intervals.
\end{flushleft}

>>>>

In this section we will start by describing how we estimated the effective 
reproductive number, $R_t$, relative to the global dengue cases, and its 
posterior probability distribution. 
We then proceed to describe the SIR model 
used to represent the global incidence and how the $R_t$ is integrated into the 
model to allow for time varying transmission. 
Then we describe the Bayesian 
estimation methodology applied to find the posterior probability distributions 
of the susceptibles to the main circulating Dengue viruses for each epidemic, 
using Dengue incidence time series for Rio de Janeiro from 1996 to 2014.
In the last subsection we describe how we estimated the Attack ratio of each 
epidemic from the estimated susceptibility and observed incidence.

@@

\begin{table}[!ht]
\caption{
\bf{Median Attack ration calculated according to (\ref{eq:AR2})}}
\begin{center}
\begin{tabular}{l|r}
\hline
Year & Median Attack Ratio (\%) \\
\hline
1996 & \textbf{38.64} (17.18-54.19)\\
1997 & \textbf{87.31} (73.83-87.31)\\
1998 & \textbf{49.86} (49.19-49.86)\\
1999 & \textbf{10.76} (3.72-20.24)\\
2000 & \textbf{25.49} (24.47-26.98)\\
2001 & \textbf{48.12} (46.57-49.15)\\
2005 & \textbf{14.74} (10.23-21.38)\\
2006 & \textbf{11.22} (8.00-14.41)\\
2007 & \textbf{15.08} (14.76-15.38)\\
2008 & \textbf{13.73} (3.10-30.84)\\
2010 & \textbf{18.30} (17.34-19.33)\\
2011 & \textbf{8.59} (8.20-9.36)\\
2012 & \textbf{13.92} (12.71-14.92)\\
\hline
\end{tabular}
\begin{flushleft} We report medians and 95\% credibility intervals.
\end{flushleft}
